TacticToe: Learning the Game of Tactics

### 2018-02-07 tactictoe_jv.tex
Write some draft text

\subsection{The problem}
How a user works with an ITP and how this gives rise to a machine learning
problem.
Two ways of representing a formulas.
Definition of a tactic in \holfour. In this research, we will take the definition
that a tactic takes a goal and returns a list of goals.
Input of the prediction: goal
If a tactic produces no goals then its input goal is solved.
Define tactical etc maybe import graphic that explain how tactic works form the
presentations.

>>>>

\subsection{The problem}
% How a user works with an ITP and how this gives rise to a machine learning problem.
\todo{RK: this is just a first draft -- feel free to edit lots!}
An ITP is a development environment for the construction of formal proofs in which it is possible, but not common, to write a proof as a sequence of applications of primitive inference rules.
The common approach, however, is to use and devise high-level tools and automation that abstract over useful ways of producing proof pieces.
A specific, prevalent instance of this approach is the use of \emph{tactics} for \emph{backward} or goal-directed proof.
Here, the ITP user operates on a proof state, initially the desired conjecture, and applies tactics that transform the proof state until it is solved (or until giving up).
Each tactic performs a sound transformation of the proof state: essentially, it promises that if the resulting proof state can be solved, then so can the starting one.
This gives rise to a machine learning problem: can we learn a mapping from a given proof state to the next tactic (or sequence of tactics) that will productively advance the proof towards a solution?

Two ways of representing a formulas.
Definition of a tactic in \holfour. In this research, we will take the definition
that a tactic takes a goal and returns a list of goals.
Input of the prediction: goal
If a tactic produces no goals then its input goal is solved.
Define tactical etc maybe import graphic that explain how tactic works form the
presentations.
